toyData

### 2017-11-09 latex/article_vol3.tex
CRAN pre v10 check

\begin{figure}[tb]
\begin{center}
\frame{\includegraphics[width=7.5cm,page=2]{dataMaid_toyData.pdf}}
\frame{\includegraphics[width=7.5cm,page=3]{dataMaid_toyData.pdf}}
%\includepdf[pages={2}, pagecommand={}]{dataMaid_testData.pdf}
\end{center}
\caption{The two first pages of the report created by running \code{makeDataReport()} on the \code{toyData}
  dataset. First, a summary of the full dataset is given along with an overview of what checks were performed. Next, a summary of all the variables and whether or not they are problematic is provided. Larger versions of the pages can be seen in
  Appendix~\ref{sec:appendix1}.}
\label{fig:example1}
\end{figure}

\begin{figure}[tb]
\begin{center}
\frame{\includegraphics[width=7.5cm,page=4]{dataMaid_toyData.pdf}}
\frame{\includegraphics[width=7.5cm,page=5]{dataMaid_toyData.pdf}}
%\includepdf[pages={2}, pagecommand={}]{dataMaid_testData.pdf}
\end{center}
\caption{The third and fourth pages of the report created by running \code{makeDataReport()} on the \code{toyData}
  dataset. Here, we see a description of each variable in the dataset, consiting of a summary table, a visualization and a indication of what problems were flagged for the variable (if any). At last, a few lines of metadata about the \code{makeDataReport()} are included for enhancing reproducibility. Larger versions of the pages can be seen in
  Appendix~\ref{sec:appendix1}.}
\label{fig:example2}
\end{figure}

>>>>

\begin{figure}[tb]
\begin{center}
\frame{\includegraphics[width=7.5cm,page=2]{dataMaid_toyData_appA.pdf}}
\frame{\includegraphics[width=7.5cm,page=3]{dataMaid_toyData_appA.pdf}}
%\includepdf[pages={2}, pagecommand={}]{dataMaid_testData.pdf}
\end{center}
\caption{The two first pages of the report created by running \code{makeDataReport()} on the \code{toyData}
  dataset. First, a summary of the full dataset is given along with an overview of what checks were performed. Next, a summary of all the variables and whether or not they are problematic is provided. Larger versions of the pages can be seen in
  Appendix~\ref{sec:appendix1}.}
\label{fig:example1}
\end{figure}

\begin{figure}[tb]
\begin{center}
\frame{\includegraphics[width=7.5cm,page=4]{dataMaid_toyData_appA.pdf}}
\frame{\includegraphics[width=7.5cm,page=5]{dataMaid_toyData_appA.pdf}}
%\includepdf[pages={2}, pagecommand={}]{dataMaid_testData.pdf}
\end{center}
\caption{The third and fourth pages of the report created by running \code{makeDataReport()} on the \code{toyData}
  dataset. Here, we see a description of each variable in the dataset, consisting of a summary table, a visualization and an indication of what problems were flagged for the variable (if any). At last, a few lines of metadata about the \code{makeDataReport()} are included for enhancing reproducibility. Larger versions of the pages can be seen in
  Appendix~\ref{sec:appendix1}.}
\label{fig:example2}
\end{figure}

### 2017-11-09 latex/dataMaid_toyData.Rmd
CRAN pre v10 check

---
dataMaid: yes
title: toyData
subtitle: "Autogenerated data summary from dataMaid"
date: 2017-11-09 02:44:43
output: pdf_document
documentclass: report
header-includes:
  - \renewcommand{\chaptername}{Part}
  - \newcommand{\fullline}{\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}}
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(ggplot2)
library(pander)
```
# Data report overview
The dataset examined has the following dimensions:

@@

 *  Report creation time: Thu Nov 09 2017 02:44:43

 *  dataMaid v0.9.7.9000 [Pkg: 2017-11-08 from local (ekstroem/dataMaid@NA)]

 *  R version 3.4.1 (2017-06-30).

>>>>

---
dataMaid: yes
title: toyData
subtitle: "Autogenerated data summary from dataMaid"
date: 2017-11-09 15:41:24
output: pdf_document
documentclass: report
header-includes:
  - \renewcommand{\chaptername}{Part}
  - \newcommand{\fullline}{\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}}
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(ggplot2)
library(pander)
```
# Data report overview
The dataset examined has the following dimensions:

@@

 *  Report creation time: Thu Nov 09 2017 15:41:24

 *  dataMaid v0.9.7.9000 [Pkg: 2017-11-09 from local (ekstroem/dataMaid@NA)]

 *  R version 3.4.2 (2017-09-28).
